Field training 02 - Leaf traits measurements

### 2023-06-13 submission_2/submission_2.qmd
add description of varying equations (chlorophyll)

@@

>>>>

It is to mention that the unit of the equation from Monje & Bugbee (1992) was wrong and therefore we divided the resulting values by 10. We further recalculated the equations from Markwell et al. (1995) from $\mu mol/mm^2$ to $\mu g/mm^2$ by multiplicating the values with 0.089348898 (because the molar mass of chlorophyll A is 893.48898 g/mol).

@@

All equations yield relatively similar results (see curves 2-5), except the one from Monje & Bugbee (1992), which results in lower values.
